\section{Conclusion}

In this thesis, I have presented the progress of the \CENTREX\ experiment
towards its goal of providing an improved measurement of the upper bound on the
Schiff moment in thallium fluoride. The main contribution of this thesis work
has been to construct the beam source and the magnetic field setup in the form
of the magnetic shield with shim coils.

The introductory sections try to place our work in the context of several
parallel streams of inquiry that have been operational for the past several
decades. On the one hand, connecting with man's long-standing interest in our
place in the universe, we are interested to find out why the nature of the
matter observed to date is skewed almost entirely in favor of matter instead of
a more equal balance with antimatter. On the other extreme of scale, at all
times new microscopic theories of matter are being developed with the aim of
superseding the Standard Model in terms of accuracy or theoretical elegance.
The \CENTREX\ experiment, by executing the most precise measurement of the
Schiff moment in a thallium fluoride molecule to date, aims to improve the
current upper bounds on the strength of time-violating fundamental interactions.
These interactions are intimately linked with potential for new discoveries on
both the universe and subatomic scales.

The beam source was presented in chapter \ref{beam_source_ch}. The presentation
encompassed aspects of the beam sources exhibited in the literature, forming the
conceptual basis of of \CENTREX\ design. We went into considerable detail noting
the construction and operation of the device. We summarized the performance
characteristics of it. We discussed the state of the art in the target making
procedure, forming an essential part of the beam source operation. In the final
section, we looked at potential improvements for a future version of the beam
source, or adaptations to the current device.

The magnetic shield and shim coil setup was exhibited in chapter
\ref{mfc_chapter}. At the time we had begun the work on magnetic shielding,
there was a lack of understanding of how a passive magnetic device is able to
achieve static shielding factors of the magnitude routine observed
experimentally. The theory section of the chapter essays to connect some
observations from materials science into a coherent explanation of the shielding
factor mystery. As for the beam source, the chapter attempts to be exhaustive in
its description of the constructional details of the magnetic shield. The
performance of the shield in terms of the parameters that are relevant for this
experiment is treated in some depth in the sections that follow.

In chapter \ref{RC_chapter}, we described some early work that was necessary for
the implementation of the rotational cooling of the molecular beam, including an
estimate of the required microwave power and the vacuum window thickness to
control the reflections of the microwave beams involved. Chapters
\ref{test_int_ch}, \ref{HV_chap}, and \ref{lens_ch} address the current state of
the experimental apparatus, respectively, for a scale-model interaction region,
the high-voltage control system, and the electrostatic lens. The scaled
interaction region and electrostatic lens have been already constructed and are
now actively being integrated into and tested in the context of the molecular
beam apparatus, both requiring a source of high voltage to develop
30~kV/cm-scale electric fields.

The reader is encouraged to continue reading the fascinating material beyond
this present Conclusion, if interested in an elegant Python representation of a
molecular Hamiltonian, a pictorial representation of the beam source assembly
procedure, the custom-built electronics supporting the operation of the magnetic
shield and high-voltage systems, \gls{PMT} calibration, or microwave
metamaterial absorbers.
